\documentclass[9pt]{article}

\usepackage{extsizes}

\usepackage{multicol}
\usepackage{titlesec}

\usepackage{geometry}
\geometry{letterpaper,margin=0.5in}

\usepackage{fontspec}

\newcommand{\textjuni}[1]{{\fontspec{Junicode}#1}}

\usepackage[parfill]{parskip}

\usepackage[T1]{fontenc}
\usepackage{times}

\title{Traditional Catholic Prayers}
\date{2019-03-31}
\author{John DeCuir}

\titlespacing*{\section}
{0pt}{2ex}{1ex}
\titlespacing*{\subsection}
{0pt}{2ex}{1ex}
\titlespacing*{\paragraph}
{0pt}{2ex}{1ex}


\begin{document}

\begin{multicols}{3}

\section*{Traditional Morning Prayers}

\textit{Kneel down and making the sign of the cross, say:}

\textsc{In} the name of the Father, and of the Son, and of the Holy Ghost.
Amen.

Blessed be the holy and undivided Trinity, now and for evermore.
Amen.

\subsection*{An Act of Adoration}

\textsc{O great} God, the sovereign Lord of heaven and earth, I prostrate
myself before Thee.  With all the Angels and Saints I adore
Thee, I acknowledge Thee to be my Creator and sovereign Lord,
my first beginning and last end.  I render to Thee the homage
of my being and life.  I submit myself to Thy holy Will,
and I devote myself to Thy divine service this day and for
ever.

\paragraph{Our Father}

\textsc{Our} Father, Who art in heaven, hallowed be Thy name.
Thy kingdom come.  Thy will be done on earth, as it is in heaven.
Give us this day our daily bread.  And forgive us our trespasses,
as we forgive those who trespass against us.  And lead us not
into temptation, but deliver us from evil.  Amen.

\paragraph{Hail Mary}

\textsc{Hail}, Mary, full of grace, the Lord is with thee;
blessed art thou among women, and blessed is the fruit of
thy womb, Jesus.  Holy Mary, Mother of God, pray for us sinners,
now and at the hour of our death. Amen.

\paragraph{The Apostles' Creed}

\textsc{I believe} in God, the Father almighty, Creator of Heaven and earth,
and in in Jesus Christ, His only Son, our Lord. He was conceived by
the Holy Ghost, and born of the Virgin Mary. He suffered under Pontius
Pilate, was crucified, died and was buried. He descended into Hell.
On the third day He rose again. He ascended into Heaven, and is seated
at the right hand of God the Father Almighty. He will come again to
judge the living and the dead. I believe in the Holy Spirit, the Holy
Catholic Church, the communion of saints, the forgiveness of sins, the
resurrection of the body, and life everlasting. Amen. 

\paragraph{Act of Faith}

\textsc{O my} God! I firmly believe that Thou art one God in three Divine persons,
Father, Son, and Holy Ghost; I believe that Thy Divine Son became man,
and died for our sins, and that he will come to judge the living and the
dead. I believe these and all the truths which the Holy Catholic Church
teaches, because Thou hast revealed them, who canst neither deceive nor
be deceived.

\paragraph{Act of Hope}

\textsc{O my} God! relying on Thy infinite goodness and promises, I hope to obtain
pardon of my sins, the help of Thy grace, and life everlasting, through
the merits of Jesus Christ, my Lord and Redeemer. 

\paragraph{Act of Charity}

\textsc{O my} God! I love Thee above all things, with my whole heart and soul,
because Thou art all-good and worthy of all love. I love my neighbor as
myself for the love of Thee. I forgive all who have injured me, and ask
pardon of all whom I have injured. 

\textit{Make a firm resolution to avoid evil and to do good.}

\textsc{Adorable} Jesus! divine pattern of that perfection to which I should aspire,
I will endeavour this day to follow Thine example: to be mild, humble, chaste,
zealous, patient, charitable and resigned. Incline my heart to keep Thy
commandments. I am resolved to watch over myself with the greatest diligence,
and to live soberly, justly and piously, for the time to come. I will take
care of my words, that I may not offend with my tongue. I will turn away my
eyes that they may not see vanity; and I will be particularly attentive not
to relapse into my accustomed failings, but to struggle against them with Thy
gracious assistance. Enlighten my mind, purify my heart and guide my steps,
that I may pass all my life in Thy divine service. Amen.

\textit{In honor of the Immaculate Conception of our Blessed Lady:}

\paragraph{Hail Mary}

\textsc{Hail}, Mary, full of grace, the Lord is with thee;
blessed art thou among women, and blessed is the fruit of
thy womb, Jesus.  Holy Mary, Mother of God, pray for us sinners,
now and at the hour of our death. Amen.

\paragraph{Hail Mary}

\textsc{Hail}, Mary, full of grace, the Lord is with thee;
blessed art thou among women, and blessed is the fruit of
thy womb, Jesus.  Holy Mary, Mother of God, pray for us sinners,
now and at the hour of our death. Amen.

\paragraph{Hail Mary}

\textsc{Hail}, Mary, full of grace, the Lord is with thee;
blessed art thou among women, and blessed is the fruit of
thy womb, Jesus.  Holy Mary, Mother of God, pray for us sinners,
now and at the hour of our death. Amen.

\subsubsection*{Litany of the Holy Name of Jesus}

Lord, have mercy on us.\\
Christ, have mercy on us.\\
Lord, have mercy on us.\\
Jesus, hear us.\\
Jesus, graciously hear us.\\
God, the Father of Heaven, \textit{have mercy on us.}\\
God the Son, Redeemer of the world, \textit{have mercy on us.}\\
God, the Holy Spirit, *\\
Holy Trinity, one God,\\
Jesus, Son of the living God,\\
Jesus, Splendor of the Father,\\
Jesus, Brightness of eternal Light,\\
Jesus, King of Glory,\\
Jesus, Sun of Justice,\\
Jesus, Son of the Virgin Mary,\\
Jesus, most amiable,\\
Jesus, most admirable,\\ 
Jesus, the mighty God,\\
Jesus, Father of the world to come,\\ 
Jesus, angel of great counsel,\\
Jesus, most powerful,\\
Jesus, most patient,\\
Jesus, most obedient,\\
Jesus, meek and humble of heart,\\ 
Jesus, Lover of Chastity,\\
Jesus, our Lover,\\
Jesus, God of Peace,\\ 
Jesus, Author of Life,\\ 
Jesus, Model of Virtues,\\ 
Jesus, zealous for souls,\\
Jesus, our God,\\
Jesus, our Refuge,\\ 
Jesus, Father of the Poor,\\ 
Jesus, Treasure of the Faithful,\\
Jesus, good Shepherd,\\
Jesus, true Light,\\
Jesus, eternal Wisdom,\\ 
Jesus, infinite Goodness,\\ 
Jesus, our Way and our Life,\\ 
Jesus, joy of the Angels,\\
Jesus, King of the Patriarchs,\\ 
Jesus, Master of the Apostles,\\
Jesus, Teacher of the Evangelists,\\ 
Jesus, Strength of Martyrs,\\
Jesus, Light of Confessors,\\
Jesus, Purity of Virgins,\\
Jesus, Crown of all Saints,\\
Be merciful unto us, \textit{spare us, O Jesus.}\\
Be merciful unto us, \textit{graciously hear us, O Jesus.}\\
From all evil, \textit{Jesus, deliver us.}\\
From all sin, *\\
From Thy wrath,\\
From the snares of the devil,\\
From the spirit of fornication,\\
From everlasting death,\\
From the neglect of Thine inspirations,\\
Through the mystery of Thy holy Incarnation,\\
Through Thy Nativity,\\
Through Thine Infancy,\\
Through Thy most divine Life,\\
Through Thy Labors,\\
Through Thy Agony and Passion,\\
Through Thy Cross and Dereliction,\\
Through Thy Sufferings,\\
Through Thy Death and Burial,\\
Through Thy Resurrection,\\
Through Thine Ascension,\\
Through Thine Institution of the Most Holy Eucharist,\\
Through Thy Joys,\\
Through Thy Glory,\\
Lamb of God, who take away the sins of the world, \textit{spare us, O Jesus.}\\
Lamb of God, who take away the sins of the world, \textit{graciously hear us, O Jesus.}\\
Lamb of God, who take away the sins of the world, \textit{have mercy on us, O Jesus.}\\
Jesus, hear us.\\
Jesus, graciously hear us.\\
\textit{Let us pray.} O Lord Jesus Christ, Who has said: Ask and ye shall receive;
seek, and ye shall find; knock, and it shall be opened unto you: grant,
we beseech Thee, to us who ask the grace of Thy most divine love, that we may
love Thee with all our hearts, words and works, and never cease to praise Thee.
Make us, O Lord, to have a continual fear and love of Thy holy Name; for Thou
never ceasest to rule and govern those whom Thou doest solidly establish in Thy
love. Who livest and reignest for ever and ever. Amen.

\subsection*{Prayer to the Guardian Angel}

\textsc{Angel} of God, my Guardian dear,\\
To whom His love commits me here,\\
Ever this day be at my side,\\
To light and guard, to rule and guide.  Amen.

\subsection*{Morning Hymn: Jam Lucis Orto Sidere}

\begin{enumerate}
    \item Now that the star of light has risen, let us to God most humbly pray,
To save us from all hurtful things in all our actions of the day.
    \item To bridle and restrain our tongue, that wordy war may not resound,
To cover and protect our sight,  from dangerous follies all around.
    \item To drive iniquity away, and purify our inmost soul,
And by spare use of meat and drink, our rebel passions to control.
    \item That, when the day has sped away, and He again the night shall bring,
We may through holy abstinence, with purity His glory sing.
    \item All glory to the Father be; all praise, eternal Son to Thee;
All honour as is ever meet to God the holy Paraclete. Amen.
\end{enumerate}

\subsection*{Come to us Holy Spirit}

\textsc{Come} to us, Holy Spirit, come,\\
One with the Father and the Son,\\
Vouchsafe to dwell within our souls\\
And quickly make our hearts Thine own.\\
Let voice and mind, and heart and strength,\\
Confess and glorify Thy name,\\
And let the fire of Charity\\
Burn bright, and other hearts inflame.

\subsection*{O God, who canst not}

\textsc{O God}, Who canst not change nor fail,\\
Guiding the hours as they roll by,\\
Brightening with beam the morning pale\\
And burning in the mid-day sky;\\
Quench Thou the fires of hate and strife,\\
The wasting fever of the heart,\\
From perils guard our feeble life,\\
And to our souls Thy peace impart.

Grant this, O Father, Only Son,\\
And Holy Spirit, God of grace,\\
To Whom all glory, Three in One,\\
Be given in every time and place. Amen.

\end{multicols}

\pagebreak

\begin{multicols}{3}

\section*{Traditional Evening Prayers}

\textit{Kneel down, and say:}

In the name of the Father, and of the Son, and of the Holy Ghost.  Amen.

Blessed be the holy and undivided Trinity, now and forevermore.  Amen.

Come, O Holy Ghost! Fill the hearts of Thy faithful, and kindle in them the fire
of Thy divine love.

\textit{Let us place ourselves in the presence of God.  Humbly adore Him:}

Great God, the Lord of heaven and earth!  I prostrate myself before Thee.
With all the Angels and Saints I adore Thee.  I acknowledge Thee to be my
Creator and sovereign Lord, my first beginning and last end.  I render to Thee
the homage of my being and life.  I submit myself to Thy holy Will, and I devote
myself to Thy divine service, now and for ever.

\paragraph{Our Father}

\textsc{Our} Father, Who art in heaven, hallowed be Thy name.
Thy kingdom come.  Thy will be done on earth, as it is in heaven.
Give us this day our daily bread.  And forgive us our trespasses,
as we forgive those who trespass against us.  And lead us not
into temptation, but deliver us from evil.  Amen.

\textit{In honor of the Immaculate Conception of our Blessed Lady:}

\paragraph{Hail Mary}

\textsc{Hail}, Mary, full of grace, the Lord is with thee;
blessed art thou among women, and blessed is the fruit of
thy womb, Jesus.  Holy Mary, Mother of God, pray for us sinners,
now and at the hour of our death. Amen.

\paragraph{Hail Mary}

\textsc{Hail}, Mary, full of grace, the Lord is with thee;
blessed art thou among women, and blessed is the fruit of
thy womb, Jesus.  Holy Mary, Mother of God, pray for us sinners,
now and at the hour of our death. Amen.

\paragraph{Hail Mary}

\textsc{Hail}, Mary, full of grace, the Lord is with thee;
blessed art thou among women, and blessed is the fruit of
thy womb, Jesus.  Holy Mary, Mother of God, pray for us sinners,
now and at the hour of our death. Amen.

\paragraph{The Apostles' Creed}

\textsc{I believe} in God, the Father almighty, Creator of Heaven and earth,
and in in Jesus Christ, His only Son, our Lord. He was conceived by
the Holy Ghost, and born of the Virgin Mary. He suffered under Pontius
Pilate, was crucified, died and was buried. He descended into Hell.
On the third day He rose again. He ascended into Heaven, and is seated
at the right hand of God the Father Almighty. He will come again to
judge the living and the dead. I believe in the Holy Spirit, the Holy
Catholic Church, the communion of saints, the forgiveness of sins, the
resurrection of the body, and life everlasting. Amen. 

\paragraph{The Confiteor}

\textsc{I confess} to Almighty God, to blessed Mary ever Virgin, to blessed
Michael the Archangel, to blessed John the Baptist, to the holy Apostles Peter
and Paul, and to all the Saints, that I have sinned exceedingly in thought,
word, and deed \textit{(strike your breast thrice in token of contrition)},
through my fault, through my fault, through my most grievous fault.  Therefore I
beseech blessed Mary ever Virgin, blessed Michael the Archangel, blessed John
the Baptist, the holy Apostles Peter and Paul, and all the Saints to pray to the
Lord our God for me.\\
\textjuni{\char"211F}. May almighty God have mercy upon us, forgive us our sins,
and bring us unto life everlasting.  Amen.\\
\textjuni{\char"2123}. May the almighty and merciful Lord grant us pardon,
absolution, and remission of our sins.\\
\textjuni{\char"211F}. Amen.

\subsection*{Examination of Conscience}

\textit{Examine yourself for what sins you have committed this day, by thought,
word, deed, or omission.}

\paragraph{Act of Faith}

\textsc{O my} God! I firmly believe that Thou art one God in three Divine persons,
Father, Son, and Holy Ghost; I believe that Thy Divine Son became man,
and died for our sins, and that he will come to judge the living and the
dead. I believe these and all the truths which the Holy Catholic Church
teaches, because Thou hast revealed them, who canst neither deceive nor
be deceived.

\paragraph{Act of Hope}

\textsc{O my} God! relying on Thy infinite goodness and promises, I hope to obtain
pardon of my sins, the help of Thy grace, and life everlasting, through
the merits of Jesus Christ, my Lord and Redeemer. 

\paragraph{Act of Charity}

\textsc{O my} God! I love Thee above all things, with my whole heart and soul,
because Thou art all-good and worthy of all love. I love my neighbor as
myself for the love of Thee. I forgive all who have injured me, and ask
pardon of all whom I have injured. 

\paragraph{Act of Contrition}

\textsc{O my} God, I am heartily sorry for having offended Thee, and I detest
all my sins, because I dread the loss of heaven and the pains of hell, but most
of all because they offend Thee, my God, who art all good, and deserving of all
my love. I firmly resolve with the help of Thy grace to confess my sins, to do
penance, and to amend my life. Amen. 

\subsection*{Litany of the Blessed Virgin}

Lord, have mercy on us.\\
Christ, have mercy on us.\\
Lord, have mercy on us.\\
Christ, hear us.\\
Christ, graciously hear us.\\
God, the Father of heaven, \textit{have mercy on us.}\\
God the Son, Redeemer of the world, *\\
God the Holy Ghost,\\
Holy Trinity, one God,\\
Holy Mary, \textit{pray for us.}\\
Holy Mother of God, *\\
Holy Virgin of virgins,\\
Mother of Christ,\\
Mother of the Church\\
Mother of divine grace,\\
Mother most pure,\\
Mother most chaste,\\
Mother inviolate,\\
Mother undefiled,\\
Mother most amiable,\\
Mother most admirable,\\
Mother of good counsel,\\
Mother of our Creator,\\
Mother of our Savior,\\
Virgin most prudent,\\
Virgin most venerable,\\
Virgin most renouned,\\
Virgin most powerful,\\
Virgin most merciful,\\
Virgin most faithful,\\
Mirror of justice,\\
Seat of wisdom,\\
Cause of our joy,\\
Spiritual vessel,\\
Vessel of honor,\\
Singular vessel of devotion,\\
Mystical rose,\\
Tower of David,\\
Tower of ivory,\\
House of gold,\\
Ark of the covenant,\\
Gate of heaven,\\
Morning star,\\
Health of the sick,\\
Refuge of sinners,\\
Comforter of the afflicted,\\
Help of Christians,\\
Queen of Angels,\\
Queen of Patriarchs,\\
Queen of Prophets,\\
Queen of Apostles,\\
Queen of Martyrs,\\
Queen of Confessors,\\
Queen of Virgins,\\
Queen of all Saints,\\
Queen conceived without original sin,\\
Queen assumed into heaven,\\
Queen of the most holy Rosary\\
Queen of the family,\\
Queen of Peace,\\
Lamb of God, who takest away the sins of the world, \textit{spare us, O Lord.}\\
Lamb of God, who takest away the sins of the world, \textit{graciously hear us O Lord.}\\
Lamb of God, who takest away the sins of the world, \textit{have mercy on us.}

\textit{From the Purification to Easter and after Pentecost:}

\textjuni{\char"2123}. Pray for us, O holy Mother of God.\\
\textjuni{\char"211F}. That we may be made worthy of the promises of Christ.

\textit{Let us pray.} Grant that we Thy servants, Lord, may enjoy unfailing
health of mind and body, and through the prayers of the ever blessed Virgin Mary
in her glory, free us from our sorrows in this world and give us eternal
happiness in the next.  Through Christ our Lord.

\textjuni{\char"211F}. Amen.

\subsection*{Prayer for the Faithful Departed}

\textsc{O God!} The Creator and Redeemer of all the faithful, grant to the souls
of Thy servants departed the remission of all their sins: that through pious
supplications they may obtain that pardon which they have always desired: Who
livest and reignest world without end. Amen.

\subsection*{Prayer for a Happy Death}

\textsc{O God,} Who hast doomed all men to die, but hast concealed from all the
hour of their death, grant that I may pass my days in the practice of holiness
and justice, and that I may deserve to quit this world in the peace of a good
conscience, and in the embraces of Thy love.  Through Christ our Lord. Amen.

\subsection*{Prayer for Protection during the Night}

\textsc{Angel} of God, to whose holy care I am committed by the divine mercy,
enlighten, defend, and protect me this night from all sin and danger.  Amen.

Visit, we beseech Thee, O Lord, this habitation, and drive from it all the
snares of the enemy.  Let Thy holy Angels dwell herein to preserve us in peace;
and may Thy blessing be upon us for ever, through Christ our Lord.  Amen.

God the Father, bless us; Jesus Christ, defend and keep us; the virtue of the
Holy Ghost enlighten and sanctify us this night and forever; and may the souls
of the faithful departed rest in peace.  Amen.

Bless, O Lord, the repose I am going to take in order to renew my strength, that
I may be better able to serve Thee.  O all ye Saints and Angels! but chiefly
thou, O Mother of God! intercede for me this night and during the rest of my
life, but particularly at the hour of my death.

May the divine assistance remain always with us. Amen.

\subsection*{Ps. 129.  De Profundis}

\textit{We have committed sins: we confess we have sinned.  But God grants pardon
to him who repents.}

Out of the depths have I cried unto Thee, O Lord: Lord hear my voice.

Let Thine ears be attentive to the voice of my supplication.

If Thou, Lord, shouldst mark iniquities, O Lord, who shall stand?

But there is forgiveness with Thee: because of Thy law I wait for Thee, O Lord.

My soul waiteth on His word: my soul hopeth in the Lord.

From the morning watch even until night let Israel hope in the Lord:

For with the Lord there is mercy, and with Him is plentiful redemption.

And He shall redeem Israel, from all their iniquities.

\textjuni{\char"2123}. Eternal rest give unto them, O Lord.\\
\textjuni{\char"211F}. And let perpetual light shine upon them.\\
\textjuni{\char"2123}. May they rest in peace.\\
\textjuni{\char"211F}. Amen.

\textit{Let us pray.}  O God, the Giver of pardon and Lover of man's salvation,
we beseech Thee in Thy mercy to grant that our brethren, kinsfolk, and
benefactors who have passed out of this life may, by the intercession of blessed
Mary ever Virgin and of all Thy Saints, partake of everlasting bliss.  Through
Christ our Lord. Amen.

\subsection*{Evensong}

Sweet Savior, bless us ere we go;\\
Thy Word into our minds instill,\\
And make our lukewarm hearts to glow\\
With lowly love and fervent will.\\
\textit{Through life’s long day and death’s dark night,\\
O gentle Jesus, be our Light.}

The day is done, its hours have run,\\
And Thou hast taken count of all,\\
The scanty triumphs grace hath won,\\
The broken vow, the frequent fall.\\
\textit{Through life’s long day and death’s dark night,\\
O gentle Jesus, be our Light.}

Grant us, dear Lord, from evil ways\\
True absolution and release:\\
And bless us, more than in past days,\\
With purity and inward peace.\\
\textit{Through life’s long day and death’s dark night,\\
O gentle Jesus, be our Light.}

Do more than pardon; give us joy,\\
Sweet fear, and sober liberty,\\
And simple hearts without alloy\\
That only long to be like Thee.\\
\textit{Through life’s long day and death’s dark night,\\
O gentle Jesus, be our Light.}

Labor is sweet, for Thou hast toiled,\\
And care is light, for Thou hast cared;\\
Let not our works with self be soiled,\\
Nor in unsimple ways ensnared.\\
\textit{Through life’s long day and death’s dark night,\\
O gentle Jesus, be our Light.}

For all we love, the poor, the sad,\\
The sinful, unto Thee we call;\\
O let Thy mercy make us glad:\\
Thou art our Jesus, and our All.\\
\textit{Through life’s long day and death’s dark night,\\
O gentle Jesus, be our Light.}

Sweet Savior, bless us; night is come;\\
Through night and darkness near us be;\\
Good angels watch about our home,\\
And we are one day nearer Thee.\\
\textit{Through life’s long day and death’s dark night,\\
O gentle Jesus, be our Light.}

\subsection*{Ejaculation}

\textsc{May} the Heart of Jesus in the most Blessed Sacrament be praised,
adored, and loved with grateful affection, at every moment, in all the
tabernacles of the world, even to the end of time. Amen.

\end{multicols}

\end{document}
